My title

### 2024-03-12 paper/paper.qmd
finished draft up to result

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/help-line-homeless-death-analysis.git"
date: today
date-format: long
abstract: "This paper analyzes the influence of Central Intake Line staff efforts on the reduction of homeless death count in Toronto. Data on coded number of calls from Central Intake Call Wrap-Up Codes dataset and data on monthly homeless death count from Deaths of People Experiencing Homelessness dataset are used in generalized linear regression models to estimate the influence. We find that the staffs’ net efforts create a statistically insignificant influence on the reduction of homeless death, with specific types of efforts appearing counterproductive. This implies that, while a positive influence does exist, the impact of the Central Intake Line staff is unfortunately minimal from a statistical point of view."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

You can and should cross-reference sections and sub-sections. We use @citeR and @rohan.

@@

The goal of our modelling strategy is twofold. Firstly,...

@@

Magnitude of effect created by the helpline efforts can be estimated through linear models.

@@

Additionally, we expect a negative relationship between homeless death and the number of homeless individuals referred to shelter & the number of individuals provided with homelessness prevention information. Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.

@@

```{r}
#| label: fig-total_coded
#| fig-cap: Visualization to show correlation between number of Calls Coded (represented by the red line) and Homeless Death Counts (represented by the blue line)
#| echo: false
#| message: false

@@

If my paper were 10 pages, then should be be at least 2.5 pages. The discussion is a chance to show off what you know and what you learnt from all this.

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/help-line-homeless-death-analysis.git"
date: today
date-format: long
abstract: "This paper analyzes the influence of Central Intake Line staff efforts on the reduction of homeless death count in Toronto. Data on coded number of calls from Central Intake Call Wrap-Up Codes dataset and data on monthly homeless death count from Deaths of People Experiencing Homelessness dataset are used in generalized linear regression models to estimate the influence. We find that the staffs’ net efforts create a statistically insignificant influence on the reduction of homeless death, with specific types of efforts appearing counterproductive. This implies that while a positive influence does exist, from a statistical point of view, the impact of the Central Intake Line staff is not significantly different from non-existent."
format: pdf
toc: true
number-sections: true
bibliography: references.bib
---

@@

The City of Toronto has been consistently providing funding and staff in an effort to reduce the active homeless population within its governing district. Amongst numerous city efforts, the 24/7 helpline — Toronto Central Intake Line — was created to offer referrals to emergency shelters, sleeping accommodations, and provide general information about homelessness and prevention. [@Central_Intake_Call]. Starting in 2020, detailed data about the Central Intake Line became available on the OpenDataToronto portal [@OpenDataToronto].

The estimand of the paper focuses on examining the influence of helpline efforts on the reduction of homeless deaths in Toronto. 
Using Central Intake Call Wrap-up Codes data [@Central_Intake_Call] from OpenDataToronto [@OpenDataToronto], three different aspects of the helpline efforts were isolated: total calls coded, referral to shelter, and homelessness prevention information provided. These three key aspects were measured against the monthly cumulative death count from Deaths of People Experiencing Homelessness Data [@Homeless_Death_Count] documented by the Toronto Public Health [@TPH]. The analyses yielded an insignificant negative correlation between the net efforts of the helpline staff. The variable referral to shelter yields a positive correlation with homeless death count, whereas the effort to provide homelessness information yields a negative correlation. This implies that the net influence of helpline efforts is statistically negligible, while individual efforts can be productive or counterproductive. This examination in the net efforts and individual efforts can provide the helpline with a suggestion of which types of services or calls would be more economically efficient to allocate their labor resources on.

@@

While we can still make claims on the correlations between helpline efforts and homeless death count without modelling, regression analysis is still necessary to provide rigorous backbones for a claim's statistical significance.

@@

Magnitude of effect created by the helpline efforts can be estimated through linear models. Gaussian regression model is best suited for our analytical purposes. Other generalized linear models such as Logistic and Multilevel are not considered due to the nature of the variables in interest. Logistic regression model requires data that yields either an **yes** or **no** result, whereas multilevel model require more complexity between variables. Due to the nature of the Poisson function, the Poisson model was considered and discarded because model results in extremely small values with no evidently different interpretations.

@@

Additionally, we expect a negative relationship between homeless death and the two individual efforts: *number of homeless individuals referred to shelter*, and *number of individuals provided with homelessness prevention information*. Since both factors are coded efforts made by the helpline, both factors should also help to reduce homeless death count in Toronto.

@@

```{r}
#| label: fig-total_coded
#| fig-cap: Visualization to show correlation between number of Calls Coded and Homeless Death Counts
#| echo: false
#| message: false

@@
